A parallel general purpose multi-objective optimization framework, with application to electron beam dynamics

### 2019-03-25 paper/submission/prab.tex
small typo fix

A hallmark of the AWA facility is the flexibility to swap physical
components in the beamlines, which enables different, often novel,
accelerator research experiments to take place.  Not only do the
physical machine components change, the beam characteristics also vary
considerably to meet different needs.  The facility operates at both low
and high charge (up to 100 nC), and at high charge strong nonlinearities
require a full 3D space charge approach in simulations.  
Finding optics solutions in this regime, especially when
there are additional constraints such as the small aperture two-beam
accelerating structures, is challenging even without the quick
turnaround of the beamline configurations.  Therefore, it has been an
important research objective to develop a precise, e.g. 3D model
embedded into a multi-objective optimization framework that may be used
as a flexible platform for optimization of changing machine
configurations operated at different charge levels. While other codes,
such as GPT~\cite{gpt} and ELEGANT~\cite{elegant}, also have
integrated genetic optimization algorithms; the OPAL~\cite{opal} framework
differentiates itself by being open source (i.e. free to use), massively
parallel, and fully 3D.

>>>>

A hallmark of the AWA facility is the flexibility to swap physical
components in the beamlines, which enables different, often novel,
accelerator research experiments to take place.  Not only do the
physical machine components change, the beam characteristics also vary
considerably to meet different needs.  The facility operates at both low
and high charge (up to \SI{100}{nC}), and at high charge strong nonlinearities
require a full 3D space charge approach in simulations.  
Finding optics solutions in this regime, especially when
there are additional constraints such as the small aperture two-beam
accelerating structures, is challenging even without the quick
turnaround of the beamline configurations.  Therefore, it has been an
important research objective to develop a precise, e.g. 3D model
embedded into a multi-objective optimization framework that may be used
as a flexible platform for optimization of changing machine
configurations operated at different charge levels. While other codes,
such as GPT~\cite{gpt} and ELEGANT~\cite{elegant}, also have
integrated genetic optimization algorithms; the OPAL~\cite{opal} framework
differentiates itself by being open source (i.e. free to use), massively
parallel, and fully 3D.

### 2019-03-25 paper/submission/theor-experiment.tex
small typo fix

The first four objectives, parameters (\ref{eq:awa:p1}) to (\ref{eq:awa:p2}),
minimize the transverse ($rms_{x,y}$) beam size and transverse momentum ($rms_{px,py}$)
at the location of interest in the beam line ($s_3$, see Fig.~\ref{awa-tba}). 
Minimizing the beam size at this location is essential to 
to preventing loss of particles by scraping; 
which ensures better transmission through the wakefield structures downstream.
These structures are called Power Extractor and Transfer Structure (PETS), 
and will be located after the septum and quadrupoles in Fig.~\ref{awa-tba}.
This device is putting the tightest constraints on the beam parameters.  
The aperture diameter is \SI{17.6}{mm} and the bunch length should be below \SI{2}{mm}
to facilitate large power extraction~\cite{PETSeq}.   
Less divergence in the beam (lower transverse momentum spread) 
reduces growth of transverse beam size after the focal point (location of min beam size).
This reduces halo by ensuring the beam is not over focused through a hard waist.
The momentum spread is also critical to preventing large growth during transport. 
All of these factors help with transmission downstream.

>>>>

The first four objectives, parameters (\ref{eq:awa:p1}) to (\ref{eq:awa:p2}),
minimize the transverse ($rms_{x,y}$) beam size and transverse momentum ($rms_{px,py}$)
at the location of interest in the beam line ($s_3$, see Fig.~\ref{awa-tba}). 
Minimizing the beam size at this location is essential to 
preventing loss of particles by scraping; 
which ensures better transmission through the wakefield structures downstream.
These structures are called Power Extractor and Transfer Structure (PETS), 
and will be located after the septum and quadrupoles in Fig.~\ref{awa-tba}.
This device is putting the tightest constraints on the beam parameters.  
The aperture diameter is \SI{17.6}{mm} and the bunch length should be below \SI{2}{mm}
to facilitate large power extraction~\cite{PETSeq}.   
Less divergence in the beam (lower transverse momentum spread) 
reduces growth of transverse beam size after the focal point (location of min beam size).
This reduces halo by ensuring the beam is not over focused through a hard waist.
The momentum spread is also critical to preventing large growth during transport. 
All of these factors help with transmission downstream.
